Spatial variation of the native colon microbiota in healthy adults

### 2018-02-08 submission/manuscript.Rmd
model updates

```{r otu_barplot, echo=FALSE}
source('../code/Sum_OTU_by_Tax.R')
source('../code/sum_shared.R')

#use this code to assign phyla to each OTU in the shared file 
sub <- '../data/mothur/kws_final.an.0.03.subsample.shared'
shared_phyla <- get_tax_level_shared(sub, tax, 2)
phyla_met <- merge(meta_file, shared_phyla, by.x='group', by.y='row.names')

#try to get the df organized to work as a boxplot - no median calculation 
phyla_test <- phyla_met[, c("location","Firmicutes","Bacteroidetes","Proteobacteria","Verrucomicrobia","Actinobacteria","Fusobacteria")]
subsampled_to <- 4231
RA <- function(x) 100*x/subsampled_to

phyla_RA <- data.frame(phyla_test[1], apply(phyla_test[2:ncol(phyla_test)],2, RA))
phylaRAnames <- colnames(phyla_RA[,1:7])
phyla_RAmelt <- melt(phyla_RA[, phylaRAnames], id.vars=1)

@@

#update this to just be importing end files off of optimization scripts to pull AUCs from
```

>>>>

@@

#update this to just be importing end files off of optimization scripts to pull AUCs from
